---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# abcR

*abcR* is a wrapper for the *[abcjs](https://abcjs.net/])* javascript library.

## Status

*abcR* is currently in alpha and hence its functionality and interface
are subject to change.
The package still needs to be documented.

## Installation

You can install *abcR* from Github by entering the following into 
your R terminal:

```r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("pmcharrison/abcR")
```

## Example usage

Displaying a pitch-class set within an R markdown file:

```{r, include = TRUE}
library(abcR)
abc_html_from_pc_set(c(0, 4, 9))
```

Displaying an *abc* file:

```{r, include = TRUE}
abc_html_from_file(system.file("examples/example-song.abc",
                               package = "abcR"))
```

Displaying a pitch-class set within RStudio:

```r
abc_view_pc_set(c(0, 4, 7))
```

## Authors

- *abcR*: Peter M. C. Harrison
- *absjs*: Paul Rosen and Gregory Dyke

## License

Both *abcR* and *abcjs* are released under the MIT license.
